---
title: United Nations Votes
subtitle: My first Quarto file
author: Gabriel Stomberg-Fannon
date: today
format: html
---

# Introduction

How do various countries vote in the United Nations General Assembly, how have their voting patterns evolved throughout time, and how similarly or differently do they view certain issues? Answering these questions (at a high level) is the focus of this analysis.

## Packages

We will use the **tidyverse**, **lubridate**, and **scales** packages for data wrangling and visualization, and the **DT** package for interactive display of tabular output, and the **unvotes** package for the data.

```{r}
#| label: load-packages
#| message: false
#| warning: false

library(tidyverse)
library(lubridate)
library(scales)
library(DT)
library(unvotes)
```



## Data

The data we're using originally come from the **unvotes** package. In the chunk below we modify the data by joining the various data frames provided in the package to help you get started with the analysis.

```{r}
#| message: false
#| warning: false
unv <- unvotes::un_votes %>%
  inner_join(un_roll_calls, by = "rcid") %>%
  inner_join(un_roll_call_issues, by = "rcid")
```

# UN voting patterns

Let's create a data visualisation that displays how the voting record of the UK & NI changed over time on a variety of issues, and compares it to two other countries: US and Turkey.

```{r}
#| label: plot-yearly-yes-issue
#| fig-width: 10
#| fig-height: 6

unv %>%
  filter(country %in% c("Turkey", "United States", "United Kingdom")) %>%
  mutate(year = year(date)) %>%
  group_by(country, year, issue) %>%
  summarize(percent_yes = mean(vote == "yes")) %>%
  ggplot(mapping = aes(x = year, y = percent_yes, color = country)) +
  geom_point(alpha = 0.4) +
  geom_smooth(method = "loess", se = FALSE) +
  facet_wrap(~issue) +
  scale_y_continuous(labels = percent) +
  labs(
    title = "Percentage of 'Yes' votes in the UN General Assembly",
    subtitle = "1946 to 2019",
    y = "% Yes",
    x = "Year",
    color = "Country"
  )
```

**1. Write 1-2 sentences here about what you learned from these plots**

Turkey voted yes a lot more than the UK and US on every issue beginning soon after 1946. Additionally, the UK almost always voted yes more than the US on every issue after the 1960s. This also is a very complicated subject that these graphs do not tell the whole story to.

We can easily change which countries are being plotted by changing which countries the code above `filter`s for. Note that the country name should be spelled and capitalized exactly the same way as it appears in the data. See the [Appendix](#appendix) for a list of the countries in the data.

**2. Customize the plot**
Choose different countries to explore. Copy the entire code chunk from above to below this line, edit the countries and re-render. Write a few sentences comparing these countries to the ones above. 

```{r}
#| fig-width: 10
#| fig-height: 6

unv %>%
  filter(country %in% c("Benin", "Canada", "Japan")) %>%
  mutate(year = year(date)) %>%
  group_by(country, year, issue) %>%
  summarize(percent_yes = mean(vote == "yes")) %>%
  ggplot(mapping = aes(x = year, y = percent_yes, color = country)) +
  geom_point(alpha = 0.4) +
  geom_smooth(method = "loess", se = FALSE) +
  facet_wrap(~issue) +
  scale_y_continuous(labels = percent) +
  labs(
    title = "Percentage of 'Yes' votes in the UN General Assembly",
    subtitle = "1946 to 2019",
    y = "% Yes",
    x = "Year",
    color = "Country"
  )
```

Benin voted yes A LOT more on every issue than either Japan or Canada almost for the entire time span studied, with the exception of Human rights and Palestinian conflict issues. Canada had an incredibly sharp decline on voting yes for the Palestinian conflict issues immediately after 2000 to now consistently voting 100% no on the issue. Other than that, Japan and Canada have very similar voting trends across all other issues during the entire time period.

## References

1.  David Robinson (2017). [unvotes](https://CRAN.R-project.org/package=unvotes): United Nations General Assembly Voting Data. R package version 0.2.0.
2.  Erik Voeten "Data and Analyses of Voting in the UN General Assembly" Routledge Handbook of International Organization, edited by Bob Reinalda (published May 27, 2013).
3.  Much of the analysis has been modeled on the examples presented in the [unvotes package vignette](https://cran.r-project.org/web/packages/unvotes/vignettes/unvotes.html).